Progress Report for CSS 586 Course Project: \\ Modeling Latent Patterns in Music

### 2021-04-25 papers/progress/alex/progress-alex.tex
paper and deps updates

\begin{document}
\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}
\title{Progress Report for CSS 586: \\
Modeling Latent Patterns in Music}

@@

\begin{abstract}
This report explores recent research in modeling music with deep learning and
provides a progress report on a course project to train a generative model of
classical music on the MusicNet dataset.
\end{abstract}

\keywords{deep learning, neural networks, music}

@@

@@

>>>>

\begin{document}
\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}
\title{Progress Report for CSS 586 Course Project: \\
Modeling Latent Patterns in Music}

@@

\begin{abstract}
This report explores recent research in modeling music with deep learning and
provides a progress report on a course project to train a generative model of
classical and popular music on the MusicNet and Lakh MIDI datasets.
\end{abstract}

\keywords{deep learning, sequence learning, generative modeling, recurrent neural networks, music, MIDI}

@@

MuseGAN  \cite{dong2017musegan}.

@@

\subsection{Datasets}
